---
title: "October Push"
author: "Julian Bernado"
---

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
set.seed(1)
```

```{r}
#| label: libraries
#| include: false
pkgs <- c("rmarkdown", "readr", "dplyr")

missing <- pkgs[!sapply(pkgs, requireNamespace, quietly = TRUE)]
if (length(missing)) install.packages(missing)

invisible(lapply(pkgs, library, character.only = TRUE))
```

```{r}
#| label: data
#| include: false
df <- read_csv("data/dummy.csv")
```

I'm getting serious about trying to wrap up the work for this project by early November. But with the sparseness of my fully-focused sustained attention on a full-time basis, it's been a bit hard keeping it all in my head. I wanted to get everything down in a format that could serve like a textbook for finishing writing all the code and then writing the paper. I want to do it in this format rather than plain notes so that I can have a browsable, densely linked set of notes that may include typeset math or code.

## Main pages
* [where we're at](whereweat)
* [Notation](notation)
* [matchAhead procedure](matchAhead)
* [Pimentel procedure](pimentel)



